---
title: "TAP in TE"
output:
  pdf_document: default
  html_document: default
---

```{r load-packages, include=FALSE}
#install.packages("dplyr")
#install.packages("car")
#install.packages("effsize")
#install.packages("agricolae")
#install.packages("multcomp")
#install.packages("ggplot2")
#install.packages("jtools")
#install.packages("ggpubr")
#install.packages("numform")

library(dplyr)
library(car)
library(effsize)
library(agricolae)
library(multcomp)
library(ggplot2)
library(jtools)
library(ggpubr)
library(numform)

tap1 <- read.csv("TAPinTE_Exp1_Data.csv")
tap2 <- read.csv("TAPinTE_Exp2_Data.csv")
tap3 <- read.csv("TAPinTE_Exp3_Data.csv")
tap4 <- read.csv("TAPinTE_Exp4_Data.csv")

knitr::opts_chunk$set(echo = TRUE)
```

##TAP1
###TAP1 P2 performance: IS vs. R
* R > IS
```{r}
tap1_test <- tap1[tap1$Activity == "Test",]

tap1_test %>%
    group_by(P2) %>%
    summarise(M = mean(P2AC),
              SE = sd(P2AC)/sqrt(length(P2AC)))

## t test assumptions - did not check normal distribution
## t test assumptions - Levene's test - check equal variance 
leveneTest(P2AC ~ P2, data = tap1_test)
## levens test turned out to be sig, but we assume equal variance anyway

## t test
t_tap1_P2AC <- t.test(P2AC ~ P2, data = tap1_test, var.equal = T)
t_tap1_P2AC

## SED
round((0.8952991-0.9612573)/t_tap1_P2AC$statistic, digits = 3)

## effect size
tap1_IStest <- tap1_test$P2AC[tap1_test$P2 == "IS"]
tap1_Rtest <- tap1_test$P2AC[tap1_test$P2 == "R"]
cohen.d(tap1_IStest,tap1_Rtest)
```

###TAP1 P3 performance (all): test vs. study; P2IS vs. P2R; P3IS vs. P3R
```{r}
## main effect of activity descriptives
#tap1 %>%
    #group_by(Activity) %>%
    #summarise(M = mean(P3AC),
              #SE = sd(P3AC)/sqrt(length(P3AC)))

## main effect of P2 descriptives
#tap1 %>%
    #group_by(P2) %>%
    #summarise(M = mean(P3AC),
              #SE = sd(P3AC)/sqrt(length(P3AC)))

## main effect of P3 descriptives
#tap1 %>%
    #group_by(P3) %>%
    #summarise(M = mean(P3AC),
              #SE = sd(P3AC)/sqrt(length(P3AC)))

## anova descriptives 
mean_se_exp1 <- tap1 %>%
    group_by(Activity, P2, P3) %>%
    summarise(M = mean(P3AC),
              SE = sd(P3AC)/sqrt(length(P3AC)),
              length(P3AC))
mean_se_exp1

mean_se1 <- tap1 %>%
    group_by(P2, P3) %>%
    summarise(M = mean(P3AC),
              SE = sd(P3AC)/sqrt(length(P3AC)))
mean_se1

## anova - did not check normal distribution or equal variance
options(contrasts = c("contr.sum", "contr.poly"))
tap1Uncon_lm <- lm(P3AC ~ Activity + P2 + P3 + Activity:P2 + Activity:P3 + P2:P3 + Activity:P2:P3, data=tap1)
tap1Uncon_anova <- Anova(tap1Uncon_lm, type = "III")
tap1Uncon_anova

## MSE
tap1Uncon_anova$`Sum Sq`[9]/147

## effect sizes
tap1Uncon_SST <- 0.199 + 0.386 + 0.750 + 0.001 + 0.093 + 0.000 + 0.004 + 6.649
## activity
0.199/tap1Uncon_SST
## P2
0.386/tap1Uncon_SST
## P3
0.750/tap1Uncon_SST
## Activity:P2
0.001/tap1Uncon_SST
## Activity:P3
0.093/tap1Uncon_SST
## P2:P3
0.000/tap1Uncon_SST
## Activity:P2:P3
0.004/tap1Uncon_SST

## this is the planned comparison (conceptual replication of the negative testing effect)
with(subset(tap1, P2 == "R" & P3 == "R"), t.test(P3AC ~ Activity, var.equal = T))

## relational final test
#tap1_RP3 <- tap1[tap1$P3 == "R",]
#options(contrasts = c("contr.sum", "contr.poly"))
#tap1Uncon_RP3_anova <- lm(P3AC ~ Activity + P2 + Activity:P2, data=tap1_RP3)
#Anova(tap1Uncon_RP3_anova, type = "III")

## item-specific final test
#tap1_ISP3 <- tap1[tap1$P3 == "IS",]
#options(contrasts = c("contr.sum", "contr.poly"))
#tap1Uncon_ISP3_anova <- lm(P3AC ~ Activity + P2 + Activity:P2, data=tap1_ISP3)
#Anova(tap1Uncon_ISP3_anova, type = "III")
```

###TAP1 ARC: test vs. study; P2IS vs. P2R
```{r}
tap1_ARC <- tap1[tap1$P3 == "R",]

## anova descriptives 
mean_se_arc <- tap1_ARC %>%
    group_by(Activity, P2) %>%
    summarise(M = mean(ARC),
              SE = sd(ARC)/sqrt(length(ARC)))
mean_se_arc

## anova assumptions - did not check normal distribution or equal variance
options(contrasts = c("contr.sum", "contr.poly"))
tap1ARC_lm <- lm(ARC ~ Activity + P2 + Activity:P2, data=tap1_ARC)
tap1ARC_anova <- Anova(tap1ARC_lm, type = "III")
tap1ARC_anova

## MSE
tap1ARC_anova$`Sum Sq`[5]/74

## effect sizes
tap1ARC_SST <- 0.067 + 1.663 + 0.049 + 8.979
## Activity
0.067/tap1ARC_SST
## P2
1.663/tap1ARC_SST
## Activity:P2
0.049/tap1ARC_SST

## this is the planned comparison (conceptual replication of the negative testing effect)
with(subset(tap1_ARC, P2 == "R" & P3 == "R"), t.test(ARC ~ Activity, var.equal = T))
```

##TAP1 test only
###TAP1 P3 performance (all): P2 IS vs. P2 R; P3 IS vs. P3 R
* Sig main effect of P2  
    + R P2 > IS P2  
* Sig main effect of P3  
    + IS P3 > R P3
* Non sig interaction between P2 and P3  
```{r}
## anova descriptives 
mean_se1 <- tap1_test %>%
    group_by(P2, P3) %>%
    summarise(M = mean(P3AC),
              SE = sd(P3AC)/sqrt(length(P3AC)))
mean_se1

## anova assumptions - did not check normal distribution or equal variance
options(contrasts = c("contr.sum", "contr.poly"))
tap1Uncon_test_lm <- lm(P3AC ~ P2 + P3 + P2:P3, data=tap1_test)
tap1Uncon_test_anova <- Anova(tap1Uncon_test_lm, type = "III")
tap1Uncon_test_anova

## MSE
tap1Uncon_test_anova$`Sum Sq`[5]/73

## effect sizes
tap1Uncon_test_SST <- 0.212 + 0.682 + 0.002 + 2.749
## P2
0.212/tap1Uncon_test_SST
## P3
0.682/tap1Uncon_test_SST
## P2:p3
0.002/tap1Uncon_test_SST

## relational final test
#with(subset(tap1_test,P3=="R"),t.test(P3AC~P2,var.equal=T))
#with(subset(tap1_test,P3=="R"),cohen.d(P3AC~P2))

## item-specific final test
#with(subset(tap1_test,P3=="IS"),t.test(P3AC~P2, var.equal=T))
#with(subset(tap1_test,P3=="IS"),cohen.d(P3AC~P2))
```

###TAP1 P3 performance (conditional): P2IS vs. P2R; P3IS vs. P3R
* Sig main effect of P2  
    + R P2 > IS P2  
* Sig main effect of P3  
    + IS P3 > R P3
* Non sig interaction between P2 and P3  
```{r}
## anova descriptives 
mean_se1_con <- tap1_test %>%
    group_by(P2, P3) %>%
    summarise(M = mean(P3AC_Con),
              SE = sd(P3AC_Con)/sqrt(length(P3AC_Con)))
mean_se1_con

## anova assumptions - did not check normal distribution or equal variance
options(contrasts = c("contr.sum", "contr.poly"))
tap1Con_lm <- lm(P3AC_Con ~ P2 + P3 + P2:P3, data=tap1_test)
tap1Con_anova <- Anova(tap1Con_lm, type = "III")
tap1Con_anova

## MSE
tap1Con_anova$`Sum Sq`[5]/73

## effect sizes
tap1Con_SST <- 0.176 + 0.821 + 0.005 + 2.614
## P2
0.176/tap1Con_SST
## P3
0.821/tap1Con_SST
## P2:P3
0.005/tap1Con_SST
```

##TAP2 
###TAP2 P2 performance: IS vs. R
* IS P2 > R P2  
```{r}
## t test descriptives
tap2 %>%
    group_by(P2) %>%
    summarise(M = mean(P2AC),
              SE = sd(P2AC)/sqrt(length(P2AC)))

## t test assumptions - did not check normal distribution
## t test assumptions - Levene's test
leveneTest(P2AC ~ P2, data = tap2)
## levens test turned out to be non-sig, we assume equal variance

## actual t test
t_tap2_P2AC <- t.test(P2AC ~ P2, data = tap2, var.equal = T)
t_tap2_P2AC

## SED
round((0.8962963-0.6977513)/t_tap2_P2AC$statistic, digits = 3)

## effect size
tap2_IS <- tap2$P2AC[tap2$P2 == "IS"]
tap2_R <- tap2$P2AC[tap2$P2 == "R"]
cohen.d(tap2_IS,tap2_R)
```

###TAP2 P3 performance (all): P2 IS vs. P2 R; P3 IS vs. P3 R
* Sig main effect of P2  
    + R P2 > IS P2  
* Marginally sig main effect of P3  
    + IS P3 (marginally larger) = R P3
* Sig interaction between P2 and P3  
    + For R P3, R P2 > IS P2  
    + For IS P3, IS P2 (numerically larger) = R P3  
```{r}
## anova descriptives 
mean_se2 <- tap2 %>%
    group_by(P2, P3) %>%
    summarise(M = mean(P3AC),
              SE = sd(P3AC)/sqrt(length(P3AC)))
mean_se2

## anova assumptions - did not check normal distribution or equal variance
options(contrasts = c("contr.sum", "contr.poly"))
tap2Uncon_lm <- lm(P3AC ~ P2*P3, data=tap2)
tap2Uncon_anova <- Anova(tap2Uncon_lm, type = "III")
tap2Uncon_anova

## MSE
tap2Uncon_anova$`Sum Sq`[5]/83

## effect sizes
tap2Uncon_anova$`Sum Sq`
tap2Uncon_SST <- 0.111626 + 0.091998 + 0.288732 + 2.027 ## SS Total
0.111626/tap2Uncon_SST ## P2 effect size
0.091998/tap2Uncon_SST ## P3 effect size
0.288732/tap2Uncon_SST ## interaction effect size

## Tukey HSD - see this webpage: 
## https://stats.stackexchange.com/questions/31547/how-to-obtain-the-results-of-a-tukey-hsd-post-hoc-test-in-a-table-showing-groupe
## http://www.sthda.com/english/wiki/two-way-anova-test-in-r#multiple-pairwise-comparison-between-the-means-of-groups
#P2XP3 <- with(tap2, interaction(P2, P3))
#tap2Uncon_lm2 <- lm(P3AC ~ P2XP3, data=tap2)
#tap2Uncon_lm2_HSD <- HSD.test(tap2Uncon_lm2, "P2XP3", group=TRUE, main = "TAP 2 Uncon post hoc Tukey HSD")
#tap2Uncon_lm2_HSD

#tap2Uncon_lm2_Tukey <- glht(tap2Uncon_lm2, linfct = mcp(P2XP3 = "Tukey"))
#summary(tap2Uncon_lm2_Tukey) #standard display
#TAP2Uncon_tuk_cld <- cld(TAP2Uncon_tuk) #letter-based display
#opar <- par(mai=c(1,1,1.5,1))
#plot(TAP2Uncon_tuk_cld)
#par(opar)

## relational final test
TAP2Uncon_RP3 <- with(subset(tap2,P3=="R"),t.test(P3AC~P2,var.equal=T))
TAP2Uncon_RP3
round((0.6157407-0.8029101)/TAP2Uncon_RP3$statistic, digits = 3)
with(subset(tap2,P3=="R"),cohen.d(P3AC~P2))

## item-specific final test
TAP2Uncon_ISP3 <- with(subset(tap2,P3=="IS"),t.test(P3AC~P2, var.equal=T))
TAP2Uncon_ISP3
round((0.7962963-0.7526455)/TAP2Uncon_ISP3$statistic, digits = 3)
with(subset(tap2,P3=="IS"),cohen.d(P3AC~P2))
```

###TAP2 P3 performance (conditional): P2 IS vs. P2 R; P3 IS vs. P3 R
* Sig main effect of P2  
    + R P2 > IS P2  
* Marginally sig main effect of P3  
    + IS P3 (marginally larger) = R P3
* Sig interaction between P2 and P3  
    + For R P3, R P2 > IS P2  
    + For IS P3, IS P2 (numerically larger) = R P3  
```{r}
## anova descriptives 
mean_se2_con<-tap2 %>%
    group_by(P2, P3) %>%
    summarise(M = mean(P3AC_Con),
              SE = sd(P3AC_Con)/sqrt(length(P3AC_Con)))
mean_se2_con

## anova assumptions - did not check normal distribution or equal variance
options(contrasts = c("contr.sum", "contr.poly"))
tap2Con_lm <- lm(P3AC_Con ~ P2 + P3 + P2:P3, data=tap2)
tap2Con_anova <- Anova(tap2Con_lm, type = "III")
tap2Con_anova

## MSE
tap2Con_anova$`Sum Sq`[5]/83

## effect sizes
tap2Con_anova$`Sum Sq`
tap2Con_SST <- 0.15132 + 0.08276 + 0.36544 + 1.940 ## SS Total
0.15132/tap2Con_SST ## P2 effect size
0.08276/tap2Con_SST ## P3 effect size
0.36544/tap2Con_SST ## interaction effect size

## Tukey HSD
#P2XP3 <- with(tap2, interaction(P2, P3))
#tap2Con_lm2 <- lm(P3AC_Con ~ P2XP3, data=tap2)
#tap2Con_lm2_HSD <- HSD.test(tap2Con_lm2, "P2XP3", group=TRUE, main = "TAP2 Con post hoc Tukey HSD")
#tap2Con_lm2_HSD

#TAP2Con_lm2_Tukey <- glht(tap2Con_lm2, linfct = mcp(P2XP3 = "Tukey"))
#summary(TAP2Con_lm2_Tukey) ## standard display
#TAP2Con_tuk_cld <- cld(TAP2Con_tuk) ## letter-based display
#opar <- par(mai=c(1,1,1.5,1))
#plot(TAP2Con_tuk_cld)
#par(opar)

## relational final test
TAP2Con_RP3 <- with(subset(tap2,P3=="R"),t.test(P3AC_Con~P2,var.equal=T))
TAP2Con_RP3
round((0.6179939-0.8313835)/TAP2Con_RP3$statistic, digits = 3)
with(subset(tap2,P3=="R"),cohen.d(P3AC_Con~P2))

## item-specific final test
TAP2Con_ISP3 <- with(subset(tap2,P3=="IS"),t.test(P3AC_Con~P2, var.equal=T))
TAP2Con_ISP3
round((0.8096223-0.7633331)/TAP2Con_ISP3$statistic, digits = 3)
with(subset(tap2,P3=="IS"),cohen.d(P3AC_Con~P2))
```

##TAP3
###TAP3 P2 performance: IS vs. R
* R P2 > IS P2  
```{r}
## t test descriptives
tap3 %>%
    group_by(P2) %>%
    summarise(M = mean(P2AC),
              SE = sd(P2AC)/sqrt(length(P2AC)))

## t test assumptions - did not check normal distribution
## t test assumptions - Levene's test
leveneTest(P2AC ~ P2, data = tap3)
## levens test turned out to be non-sig, we assume equal variance

## actual t test
t_tap3_P2AC <- t.test(P2AC ~ P2, data = tap3, var.equal = T)
t_tap3_P2AC

## SED
round((0.4285714-0.7080499)/t_tap3_P2AC$statistic, digits = 3)

## effect size
tap3_IS <- tap3$P2AC[tap3$P2 == "IS"]
tap3_R <- tap3$P2AC[tap3$P2 == "R"]
cohen.d(tap3_IS,tap3_R)
```

###TAP3 P3 performance (all): P2 IS vs. P2 R; P3 IS vs. P3 R
* Sig main effect of P2
    + R P2 > IS P2
* Marginal non-sig main effect of P3  
    + IS P3 (numerically larger) = R P3
* Non-sig interaction between P2 and P3  
```{r}
## anova descriptives 
mean_se3<-tap3 %>%
    group_by(P2, P3) %>%
    summarise(M = mean(P3AC),
              SE = sd(P3AC)/sqrt(length(P3AC)))
mean_se3

## anova assumptions - did not check normal distribution or equal variance
options(contrasts = c("contr.sum", "contr.poly"))
tap3Uncon_lm <- lm(P3AC ~ P2 + P3 + P2:P3, data=tap3)
tap3Uncon_anova <- Anova(tap3Uncon_lm, type = "III")
tap3Uncon_anova

## MSE
tap3Uncon_anova$`Sum Sq`[5]/94

## effect sizes
tap3Uncon_SST <- 0.959 + 0.118 + 0.000 + 4.002
## P2
0.959/tap3Uncon_SST
## P3
0.118/tap3Uncon_SST
## P2:p3
0.000/tap3Uncon_SST

## relational final test
#with(subset(tap3,P3=="R"),t.test(P3AC~P2,var.equal=T))
#with(subset(tap3,P3=="R"),cohen.d(P3AC~P2))

## item-specific final test
#with(subset(tap3,P3=="IS"),t.test(P3AC~P2, var.equal=T))
#with(subset(tap3,P3=="IS"),cohen.d(P3AC~P2))
```

###TAP3 conditional P3 performance: P2 IS vs. P2 R; P3 IS vs. P3 R
* Sig main effect of P2
    + R P2 > IS P2
* Sig main effect of P3  
    + IS P3 > R P3
* Marginal non-sig interaction between P2 and P3 
    + For R P3, R P2 > IS P2  
    + For IS P3, R P2 (numerically larger) = IS P2  
```{r}
## anova descriptives
mean_se3_con<-tap3 %>%
    group_by(P2, P3) %>%
    summarise(M = mean(P3AC_Con),
              SE = sd(P3AC_Con)/sqrt(length(P3AC_Con)))
mean_se3_con

## anova assumptions - did not check normal distribution or equal variance
options(contrasts = c("contr.sum", "contr.poly"))
tap3Con_lm <- lm(P3AC_Con ~ P2 + P3 + P2:P3, data=tap3)
tap3Con_anova <- Anova(tap3Con_lm, type = "III")
tap3Con_anova

## MSE
tap3Con_anova$`Sum Sq`[5]/94

## effect sizes
tap3Con_SST <- 0.189 + 0.373 + 0.106 + 2.608
0.189/tap3Con_SST
0.373/tap3Con_SST
0.106/tap3Con_SST

## relational final test
with(subset(tap3,P3=="R"),t.test(P3AC_Con~P2,var.equal=T))
with(subset(tap3,P3=="R"),cohen.d(P3AC_Con~P2))

## item-specific final test
with(subset(tap3,P3=="IS"),t.test(P3AC_Con~P2, var.equal=T))
with(subset(tap3,P3=="IS"),cohen.d(P3AC_Con~P2))
```

##TAP4
###TAP4 P2 performance: IS vs. R
* R P2 (numerically larger) = IS P2  
```{r}
## t test descriptives - 2 conditions
tap4 %>%
    group_by(P2) %>%
    summarise(M = mean(P2AC),
              SE = sd(P2AC)/sqrt(length(P2AC)))

## t test assumptions - did not check normal distribution
## t test assumptions - Levene's test
leveneTest(P2AC ~ P2, data = tap4)
## levens test turned out to be non-sig, we assume equal variance

## actual t test
t_tap4_P2AC <- t.test(P2AC ~ P2, data = tap4, var.equal = T)
t_tap4_P2AC

## SED
round((0.4622222-0.4895530)/t_tap4_P2AC$statistic, digits = 3)

## effect size
tap4_IS <- tap4$P2AC[tap4$P2 == "IS"]
tap4_R <- tap4$P2AC[tap4$P2 == "R"]
cohen.d(tap4_IS,tap4_R)
```

###TAP4 P3 performance (all): P2 IS vs. P2 R; P3 IS vs. P3 R
* Non-sig main effect of P2  
* Non-sig main effect of P3  
* Sig interaction between P2 and P3  
    + For R P3, R P2 > IS P2  
    + For IS P3, IS P2 (numerically larger) = R P3  
```{r}
## anova descriptives - 4 conditions
mean_se4<-tap4 %>%
    group_by(P2, P3) %>%
    summarise(M = mean(P3AC),
              SE = sd(P3AC)/sqrt(length(P3AC)))
mean_se4

## anova assumptions - did not check normal distribution or equal variance
options(contrasts = c("contr.sum", "contr.poly"))
tap4Uncon_lm <- lm(P3AC ~ P2 + P3 + P2:P3, data=tap4)
tap4Uncon_anova <- Anova(tap4Uncon_lm, type = "III")
tap4Uncon_anova

## MSE
tap4Uncon_anova$`Sum Sq`[5]/95

## effect sizes
tap4Uncon_SST <- 0.044 + 0.021 + 0.434 + 5.703
## p2
0.044/tap4Uncon_SST
## p3
0.021/tap4Uncon_SST
## p2:p3
0.434/tap4Uncon_SST

## Tukey HSD
#TAP4_P2XP3 <- with(tap4, interaction(P2, P3))
#tap4Uncon_lm2 <- lm(P3AC ~ TAP4_P2XP3, data=tap4)
#tap4Uncon_lm2_HSD <- HSD.test(tap4Uncon_lm2, "TAP4_P2XP3", group=TRUE, main = "test")
#tap4Uncon_lm2_HSD

#TAP4Uncon_lm2_Tukey <- glht(tap4Uncon_lm2, linfct = mcp(TAP4_P2XP3 = "Tukey"))
#summary(TAP4Uncon_lm2_Tukey) ## standard display
#TAP4Uncon_tuk_cld <- cld(TAP4Uncon_tuk) ## letter-based display
#opar <- par(mai=c(1,1,1.5,1))
#plot(TAP4Uncon_tuk_cld)
#par(opar)

## relational final test
TAP4Uncon_RP3 <- with(subset(tap4,P3=="R"),t.test(P3AC~P2,var.equal=T))
TAP4Uncon_RP3
round((0.5349794-0.7099365)/TAP4Uncon_RP3$statistic, digits = 3)
with(subset(tap4,P3=="R"),cohen.d(P3AC~P2))

## item-specific final test
TAP4Uncon_ISP3 <- with(subset(tap4,P3=="IS"),t.test(P3AC~P2, var.equal=T))
TAP4Uncon_ISP3
round((0.6968599-0.6064815)/TAP4Uncon_ISP3$statistic, digits = 3)
with(subset(tap4,P3=="IS"),cohen.d(P3AC~P2))
```

###TAP4 P3 performance (conditional): P2 IS vs. P2 R times P3 IS vs. P3 R
* Non-sig main effect of P2  
* Non-sig main effect of P3  
* Sig interaction between P2 and P3  
    + For R P3, R P2 > IS P2  
    + For IS P3, IS P2 > R P3  
```{r}
## anova descriptives - 4 conditions
tap4_Con <- tap4[is.na(tap4$P3AC_Con) == FALSE, ]

mean_se4_con<-tap4_Con %>%
    group_by(P2, P3) %>%
    summarise(M = mean(P3AC_Con),
              SE = sd(P3AC_Con)/sqrt(length(P3AC_Con)))
mean_se4_con

## anova assumptions - did not check normal distribution or equal variance
options(contrasts = c("contr.sum", "contr.poly"))
tap4Con_lm <- lm(P3AC_Con ~ P2 + P3 + P2:P3, data=tap4)
tap4Con_anova <- Anova(tap4Con_lm, type = "III")
tap4Con_anova

## MSE
tap4Con_anova$`Sum Sq`[5]/94

## effect sizes
tap4Con_SST <- 0.041 + 0.000 + 0.878 + 3.647
## p2
0.041/tap4Con_SST
## p3
0.000/tap4Con_SST
## p2:p3
0.878/tap4Con_SST

## Tukey HSD
#TAP4_P2XP3 <- with(tap4, interaction(P2, P3))
#tap4Con_lm2 <- lm(P3AC_Con ~ TAP4_P2XP3, data=tap4)
#tap4Con_lm2_HSD <- HSD.test(tap4Con_lm2, "TAP4_P2XP3", group=TRUE, main = "test")
#tap4Con_lm2_HSD

#TAP4Con_lm2_Tukey <- glht(tap4Con_lm2, linfct = mcp(TAP4_P2XP3 = "Tukey"))
#summary(TAP4Con_lm2_Tukey) ## standard display
#TAP4Con_tuk_cld <- cld(TAP4Con_tuk) ## letter-based display
#opar <- par(mai=c(1,1,1.5,1))
#plot(TAP4Con_tuk_cld)
#par(opar)

## relational final test
TAP4Con_RP3 <- with(subset(tap4,P3=="R"),t.test(P3AC_Con~P2,var.equal=T))
TAP4Con_RP3
round((0.6961652-0.8449912)/TAP4Con_RP3$statistic, digits = 3)
with(subset(tap4,P3=="R"),cohen.d(P3AC_Con~P2))

## item-specific final test
TAP4Con_ISP3 <- with(subset(tap4,P3=="IS"),t.test(P3AC_Con~P2, var.equal=T))
TAP4Con_ISP3
round((0.8857489-0.6552107)/TAP4Con_ISP3$statistic, digits = 3)
with(subset(tap4,P3=="IS"),cohen.d(P3AC_Con~P2))
```

##All graph
```{R}
allexps<-
    data.frame(rbind(mean_se1,mean_se2,mean_se3,mean_se4,
                     mean_se1_con,mean_se2_con,mean_se3_con,mean_se4_con),
               Experiment=rep(c(rep("Experiment 1",4),rep("Experiment 2",4),
                                rep("Experiment 3",4),rep("Experiment 4",4)),2),
               Analysis=c(rep("All",16),rep("Conditional",16)))

#head(allexps)

## this corresponds to Figure 3
allexps <- allexps %>%
    mutate(newP2 = ifelse(P2 == "IS", "Randomized", "Categorized"),
           newP3 = ifelse(P3 == "IS", "Randomized", "Categorized"),
           processing = ifelse(P2 == "IS" & P3 == "IS", "IS-IS",
                               ifelse(P2 == "IS" & P3 == "R", "IS-R",
                                      ifelse(P2 == "R" & P3 == "IS", "R-IS", "R-R"))),
           newM = numform::f_num(M, digits = 2),
           newSE = paste0("(", numform::f_num(SE, digits = 2), ")"))
#head(allexps)

allexps$newP2 <- factor(allexps$newP2, levels = c("Randomized", "Categorized"))
allexps$newP3 <- factor(allexps$newP3, levels = c("Randomized", "Categorized"))
#head(allexps)

## this is the new graph
allexps[allexps$Analysis == "All",] %>%
    ggplot(aes(x=newP3,y=M,fill=newP2))+
    geom_bar(stat="identity",position="dodge")+
    facet_wrap(~Experiment, ncol = 2)+ 
    geom_errorbar(aes(ymin=M-SE,ymax=M+SE),width=0.2,position=position_dodge(0.9))+
    labs(x="Final Test", y="\nProportion Recalled",
         fill="Practice Test")+
    scale_y_continuous(breaks = seq(0.00, 1.00, 0.10), limits = c(0.00, 1.00), 
                       labels = numform::ff_num(zero = 0)) +
    scale_fill_manual(values = c("#696969","#D3D3D3")) +
    geom_text(aes(label=newM), vjust = -2.7, #1.5 + 1.2
              color="black", size=4, 
              position = position_dodge(0.9)) +
    geom_text(aes(label=newSE), vjust = -1.5, #no space between dot is 1.5
              color="black", size=4,
              position = position_dodge(0.9)) +
    geom_text(aes(label = processing, y = 0.04),
              color = "black", size = 4,
              position = position_dodge(0.9)) +
    theme_apa()+
    theme(panel.border = element_rect(),
          axis.title=element_text(size = 12, face = "bold"),
          axis.text=element_text(size = 12),
          strip.text.x=element_text(size = 12),
          legend.title=element_text(size = 12, face = "bold"), 
          legend.text=element_text(size = 12),
          legend.key.height = unit(0.25, "inches"),
          legend.key.width = unit(0.25, "inches"),
          legend.position = "bottom", 
          legend.box.background = element_rect(), #default size is 0.5
          axis.text.x = element_text(colour = ifelse(allexps$newP3=="Randomized","#585858","#B8B8B8")),
          axis.text.y = element_text(color = "black"))
#ggsave("*AllPlots_All_062019.pdf", width = 6.5, height = 7.4, dpi = 600)
```

##Conditional graph
```{r}
## this is the new graph
AllPlots_Conditional <- allexps[allexps$Analysis == "Conditional",] %>%
    ggplot(aes(x=newP3,y=M,fill=newP2))+
    geom_bar(stat="identity",position="dodge")+
    facet_wrap(~Experiment, ncol = 2)+ 
    geom_errorbar(aes(ymin=M-SE,ymax=M+SE),width=0.2,position=position_dodge(0.9))+
    labs(x="Final Test", y="Proportion Recalled\n(Conditional)",
         fill="Practice Test")+
    scale_y_continuous(breaks = seq(0.00, 1.00, 0.10), limits = c(0.00, 1.00),
                       labels = numform::ff_num(zero = 0)) +
    scale_fill_manual(values = c("#696969","#D3D3D3")) +
    geom_text(aes(label=newM), vjust = -2.7, 
              color="black", size=4, 
              position = position_dodge(0.9)) +
    geom_text(aes(label=newSE), vjust = -1.5, 
              color="black", size=4,
              position = position_dodge(0.9)) +
    geom_text(aes(label = processing, y = 0.04),
              color = "black", size = 4,
              position = position_dodge(0.9)) +
    theme_apa()+
    theme(panel.border = element_rect(),
          axis.title=element_text(size = 12, face = "bold"),
          axis.text=element_text(size = 12),
          strip.text.x=element_text(size = 12),
          legend.title=element_text(size = 12, face = "bold"), 
          legend.text=element_text(size = 12),
          legend.key.height = unit(0.25, "inches"),
          legend.key.width = unit(0.25, "inches"),
          legend.position = "bottom", 
          legend.box.background = element_rect(), #default size is 0.5
          axis.text.x = element_text(colour = ifelse(allexps$newP3=="Randomized","#585858","#B8B8B8")),
          axis.text.y = element_text(color = "black"))
#ggsave("*AllPlots_Conditional_062019.pdf", width = 6.5, height = 7.4, dpi = 600)
```

##Exp 1 graph
```{r}
## this corresponds to Figure 2
mean_se_exp1 <- mean_se_exp1 %>%
    mutate(newM = numform::f_num(M, digits = 2),
           newSE = paste0("(", numform::f_num(SE, digits = 2),")"),
           newP2 = ifelse(P2 == "IS", "Randomized", "Categorized"),
           newP3 = ifelse(P3 == "IS", "Randomized", "Categorized"),
           processing = ifelse(P2 == "IS" & P3 == "IS", "IS-IS",
                               ifelse(P2 == "IS" & P3 == "R", "IS-R",
                                      ifelse(P2 == "R" & P3 == "IS", "R-IS", "R-R"))))
#mean_se_exp1

mean_se_exp1$newP2 <- factor(mean_se_exp1$newP2, levels = c("Randomized", "Categorized"))
mean_se_exp1$newP3 <- factor(mean_se_exp1$newP3, levels = c("Randomized", "Categorized"))
#mean_se_exp1

## this is the new graph
mean_se_exp1%>%
    ggplot(aes(x=newP3,y=M,fill=newP2))+
    geom_bar(stat="identity",position="dodge")+
    facet_grid(~Activity)+
    geom_errorbar(aes(ymin=M-SE,ymax=M+SE),width=0.2, position = position_dodge(0.9))+
    labs(x="Final Test", y="\nProportion Recalled",
         fill="Practice Task")+
    scale_y_continuous(breaks = seq(0.00, 1.00, 0.10), limits = c(0.00, 1.00),
                       labels = numform::ff_num(zero = 0)) +
    scale_fill_manual(values = c("#696969","#D3D3D3")) +
    geom_text(aes(label=newM), vjust = -2.9, 
              color="black", size=4, 
              position = position_dodge(0.9)) +
    geom_text(aes(label=newSE), vjust = -1.7, 
              color="black", size=4, 
              position = position_dodge(0.9)) +
    geom_text(aes(label = processing, y = 0.04),
              color = "black", size = 4,
              position = position_dodge(0.9)) +
    theme_apa()+
    theme(panel.border = element_rect(),
          axis.title=element_text(size = 12, face = "bold"),
          axis.text=element_text(size = 12),
          strip.text.x=element_text(size = 12),
          legend.title=element_text(size = 12, face = "bold"), 
          legend.text=element_text(size = 12),
          legend.key.height = unit(0.25, "inches"),
          legend.key.width = unit(0.25, "inches"),
          legend.position = "bottom", 
          legend.box.background = element_rect(), #default size is 0.5
          axis.text.x = element_text(color = ifelse(mean_se_exp1$newP3=="Randomized","#585858","#B8B8B8")),
          axis.text.y = element_text(color = "black"))
#ggsave("*Exp1Plots_062019.pdf", width = 6.5, height = 4.2, dpi = 600)
```

##Exp 1 ARC graph
```{r}
## this corresponds to Figure 4
mean_se_arc <- mean_se_arc %>%
    mutate(newM = numform::f_num(M, digits = 2),
           newSE = paste0("(", numform::f_num(SE, digits = 2),")"),
           newP2 = ifelse(P2 == "IS", "Randomized", "Categorized"),
           processing = ifelse(P2 == "IS", "IS-R", "R-R"))
#mean_se_arc

mean_se_arc$newP2 <- factor(mean_se_arc$newP2, levels = c("Randomized", "Categorized"))
#mean_se_arc

## this is the new graph
mean_se_arc%>%
    ggplot(aes(x=newP2,y=M,fill=Activity))+
    geom_bar(stat="identity",position="dodge")+
    geom_errorbar(aes(ymin=M-SE,ymax=M+SE),width=0.2, position = position_dodge(0.9))+
    labs(x = "Practice Task", y="\nARC Score", fill = "Activity")+
    scale_y_continuous(breaks = seq(0.00, 1.00, 0.10), limits = c(0.00, 1.00),
                       labels = numform::ff_num(zerp = 0)) +
    scale_fill_manual(values = c("#696969","#D3D3D3")) +
    geom_text(aes(label=newM), vjust = -3.7, 
              color="black", size=4, 
              position = position_dodge(0.9)) +
    geom_text(aes(label=newSE), vjust = -2.5, 
              color="black", size=4, 
              position = position_dodge(0.9)) +
    geom_text(aes(label = processing, y = 0.04),
              color = "black", size = 4,
              position = position_dodge(0.9)) +
    theme_apa() +
    theme(panel.border = element_rect(),
          axis.title=element_text(size = 12, face = "bold"),
          axis.text=element_text(size = 12),
          strip.text.x=element_text(size = 12),
          legend.title=element_text(size = 12, face = "bold"), 
          legend.text=element_text(size = 12),
          legend.key.height = unit(0.25, "inches"),
          legend.key.width = unit(0.25, "inches"),
          legend.position = "bottom", 
          legend.box.background = element_rect(), #default size is 0.5
          axis.text.x = element_text(color = "black"),
          axis.text.y = element_text(color = "black"))
#ggsave("*ARCPlots_062019.pdf", width = 3.65, height = 3.92, dpi = 600)
```

